Predicting the effects of character displacement on food-web dynamics

### 2019-02-09 manuscript_ECD_model.Rmd
edits to figure legends.

```{r LS_Plot, echo=FALSE, fig.cap="\\label{fig:LS_Plot}Effect of character displacement when consumers *cannot* forage for both resources simultaneously. Different line colors correspond to the tradeoff values shown in fig. 1A. Large circles (two consumers) and triangles (one consumer) correspond to the end points of the eco-evolutionary simulation, whereas as small shapes correspond to the starting points (only in panel C). Panel (A) shows how, regardless of the tradeoff, character displacement increases the effective attack rate of the consumer community. This always resulted in a suppression of resource densities (B) and concomitant decrease in food-web stability (C). As in fig. 1, our simulations used the following parameter values: *r* = 1; *K* = 4; *e* = 0.8; *m* = 1; *A* = 2. We set an initial value of *a~ii~* = 1.2 and *a~ij~* depended on the value of *n*. We set initial consumer and resource abundances as: *R~i~* = *R~j~* = 2; *C~i~* = *C~j~* = 1."}
knitr::include_graphics("Figure_ECD_LS.pdf")
```

@@

```{r McCann_Plot, echo=FALSE, fig.cap="\\label{fig:McCann_Plot}Effect of character displacement when consumers exhibit a more realistic functional response. Different line colors correspond to the tradeoff values shown in fig. 1A. Large circles (two consumers) and triangles (one consumer) correspond to the end points of the eco-evolutionary simulation, whereas as small shapes correspond to the starting points (only in panel C). Panel (A) shows how, regardless of the tradeoff, character displacement increases the effective attack rate of the consumer community. This always resulted in a suppression of resource densities (B) and concomitant decrease in food-web stability (C). As in fig. 1, our simulations used the following parameter values: *r* = 1; *K* = 4; *e* = 0.8; *m* = 1; *A* = 2. We set an initial value of *a~ii~* = 1.2 and *a~ij~* depended on the value of *n*. We set initial consumer and resource abundances as: *R~i~* = *R~j~* = 2; *C~i~* = *C~j~* = 1."}
knitr::include_graphics("Figure_ECD_McCann.pdf")
```

@@

```{r MacArthur_Plot_asymm, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:MacArthur_Plot_asymm}Effect of character displacement when consumers can forage for both resources simultaneously. Panel (A) shows the different tradeoffs in consumer attack rates used in the simulation (green, *n* = 1.15; blue, *n* = 1; orange, *n* = 0.85). Panel (B) shows how the shape of this tradeoff affects the magnitude of character displacement and the evolution of total attack rates in the consumer community. Large circles (two consumers) and triangles (one consumer) correspond to the end points of the eco-evolutionary simulation. Panels (C) and (D) show how different tradeoffs indirectly affect total resource densities (C) and food-web stability (D). Our simulations used the following parameter values: *r* = 1; *K* = 4; *e* = 0.8; *m* = 1; *A* = 2. We set an initial value of *a~ii~* = 1.2 and *a~ij~* depended on the value of *n*. We set initial consumer and resource abundances as: *R~i~* = *R~j~* = 2; *C~i~* = *C~j~* = 1."}
knitr::include_graphics("Figure_ECD_MacArthur_asymm.pdf")
```

@@

```{r LS_Plot_asymm, echo=FALSE, fig.cap="\\label{fig:LS_Plot_asymm}Effect of character displacement when consumers *cannot* forage for both resources simultaneously. Different line colors correspond to the tradeoff values shown in fig. 1A. Large circles (two consumers) and triangles (one consumer) correspond to the end points of the eco-evolutionary simulation, whereas as small shapes correspond to the starting points (only in panel C). Panel (A) shows how, regardless of the tradeoff, character displacement increases the effective attack rate of the consumer community. This always resulted in a suppression of resource densities (B) and concomitant decrease in food-web stability (C). As in fig. 1, our simulations used the following parameter values: *r* = 1; *K* = 4; *e* = 0.8; *m* = 1; *A* = 2. We set an initial value of *a~ii~* = 1.2 and *a~ij~* depended on the value of *n*. We set initial consumer and resource abundances as: *R~i~* = *R~j~* = 2; *C~i~* = *C~j~* = 1."}
knitr::include_graphics("Figure_ECD_LS_asymm.pdf")
```

@@

```{r McCann_Plot_asymm, echo=FALSE, fig.cap="\\label{fig:McCann_Plot_asymm}Effect of character displacement when consumers exhibit a more realistic functional response. Different line colors correspond to the tradeoff values shown in fig. 1A. Large circles (two consumers) and triangles (one consumer) correspond to the end points of the eco-evolutionary simulation, whereas as small shapes correspond to the starting points (only in panel C). Panel (A) shows how, regardless of the tradeoff, character displacement increases the effective attack rate of the consumer community. This always resulted in a suppression of resource densities (B) and concomitant decrease in food-web stability (C). As in fig. 1, our simulations used the following parameter values: *r* = 1; *K* = 4; *e* = 0.8; *m* = 1; *A* = 2. We set an initial value of *a~ii~* = 1.2 and *a~ij~* depended on the value of *n*. We set initial consumer and resource abundances as: *R~i~* = *R~j~* = 2; *C~i~* = *C~j~* = 1."}
knitr::include_graphics("Figure_ECD_McCann_asymm.pdf")
```

>>>>

```{r LS_Plot, echo=FALSE, fig.cap="\\label{fig:LS_Plot}Effect of character displacement when consumers *cannot* forage for both resources simultaneously. Different line colors correspond to different tradeoff values (green, *n* = 1.15; blue, *n* = 1; orange, *n* = 0.85). Large circles (two consumers) and triangles (one consumer) correspond to the end points of the eco-evolutionary simulation, whereas as small shapes correspond to the starting points (only in panel C). Panel (A) shows how, regardless of the tradeoff, character displacement increases the effective attack rate of the consumer community. This always resulted in a suppression of resource densities (B) and concomitant decrease in food-web stability (C). As in fig. 1, our simulations used the following parameter values: *r* = 1; *K* = 4; *e* = 0.8; *m* = 1; *A* = 2. We set an initial value of *a~ii~* = 1.2 and *a~ij~* depended on the value of *n*. We set initial consumer and resource abundances as: *R~i~* = *R~j~* = 2; *C~i~* = *C~j~* = 1."}
knitr::include_graphics("Figure_ECD_LS.pdf")
```

@@

```{r McCann_Plot, echo=FALSE, fig.cap="\\label{fig:McCann_Plot}Effect of character displacement when consumers exhibit a more realistic functional response. Different line colors correspond to different tradeoff values (green, *n* = 1.15; blue, *n* = 1; orange, *n* = 0.85). Large circles (two consumers) and triangles (one consumer) correspond to the end points of the eco-evolutionary simulation, whereas as small shapes correspond to the starting points (only in panel C). Panel (A) shows how, regardless of the tradeoff, character displacement increases the effective attack rate of the consumer community. This always resulted in a suppression of resource densities (B) and concomitant decrease in food-web stability (C). As in fig. 1, our simulations used the following parameter values: *r* = 1; *K* = 4; *e* = 0.8; *m* = 1; *A* = 2. We set an initial value of *a~ii~* = 1.2 and *a~ij~* depended on the value of *n*. We set initial consumer and resource abundances as: *R~i~* = *R~j~* = 2; *C~i~* = *C~j~* = 1."}
knitr::include_graphics("Figure_ECD_McCann.pdf")
```

@@

```{r MacArthur_Plot_asymm, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:MacArthur_Plot_asymm}Effect of character displacement when consumers can forage for both resources simultaneously and have an asymmetry in initial attack rates. Different line colors correspond to different tradeoff values (green, *n* = 1.15; blue, *n* = 1; orange, *n* = 0.85). Large circles (two consumers) and triangles (one consumer) correspond to the end points of the eco-evolutionary simulation, whereas as small shapes correspond to the starting points. Panel (A) shows how the shape of this tradeoff affects the magnitude of character displacement and the evolution of total attack rates in the consumer community. Panels (B) and (C) show how different tradeoffs indirectly affect total resource densities (B) and food-web stability (C). Our simulations used the following parameter values: *r* = 1; *K* = 4; *e* = 0.8; *m* = 1; *A* = 2. We set an initial value of *a~ii~* = 1.2 and *a~ij~* depended on the value of *n*. We set initial consumer and resource abundances as: *R~i~* = *R~j~* = 2; *C~i~* = *C~j~* = 1."}
knitr::include_graphics("Figure_ECD_MacArthur_asymm.pdf")
```

@@

```{r LS_Plot_asymm, echo=FALSE, fig.cap="\\label{fig:LS_Plot_asymm}Effect of character displacement when consumers *cannot* forage for both resources simultaneously and have an asymmetry in initial attack rates. Different line colors correspond to different tradeoff values (green, *n* = 1.15; blue, *n* = 1; orange, *n* = 0.85). Large circles (two consumers) and triangles (one consumer) correspond to the end points of the eco-evolutionary simulation, whereas as small shapes correspond to the starting points. Panel (A) shows how, regardless of the tradeoff, character displacement increases the effective attack rate of the consumer community. This always resulted in a suppression of resource densities (B) and concomitant decrease in food-web stability (C). As in fig. 1, our simulations used the following parameter values: *r* = 1; *K* = 4; *e* = 0.8; *m* = 1; *A* = 2. We set an initial value of *a~ii~* = 1.2 and *a~ij~* depended on the value of *n*. We set initial consumer and resource abundances as: *R~i~* = *R~j~* = 2; *C~i~* = *C~j~* = 1."}
knitr::include_graphics("Figure_ECD_LS_asymm.pdf")
```

@@

```{r McCann_Plot_asymm, echo=FALSE, fig.cap="**\\label{fig:McCann_Plot_asymm} Consumer asymmetry and Realistic Functional Response.** Effect of character displacement when consumers exhibit a more realistic functional response and have an asymmetry in initial attack rates. Different line colors correspond to different tradeoff values (green, *n* = 1.15; blue, *n* = 1; orange, *n* = 0.85). Large circles (two consumers) and triangles (one consumer) correspond to the end points of the eco-evolutionary simulation, whereas as small shapes correspond to the starting points. Panel (A) shows how, regardless of the tradeoff, character displacement increases the effective attack rate of the consumer community. This always resulted in a suppression of resource densities (B) and concomitant decrease in food-web stability (C). As in fig. 1, our simulations used the following parameter values: *r* = 1; *K* = 4; *e* = 0.8; *m* = 1; *A* = 2. We set an initial value of *a~ii~* = 1.2 and *a~ij~* depended on the value of *n*. We set initial consumer and resource abundances as: *R~i~* = *R~j~* = 2; *C~i~* = *C~j~* = 1."}
knitr::include_graphics("Figure_ECD_McCann_asymm.pdf")
```
